A large-scale analysis of racial disparities in police stops across the

### 2019-07-11 lib/paper_results.Rmd
progress

We have collected and released a dataset of 
`r pfs$basic_counts$n_stops_collected` traffic stops carried out by 
`r pfs$basic_counts$n_states_collected` state patrol agencies and 
`r pfs$basic_counts$n_cities_collected` municipal police departments.

We analyzed a unique dataset detailing 
`r pfs$basic_counts$n_stops_analyzed` traffic stops carried out by 
`r pfs$basic_counts$n_states_analyzed` state patrol agencies and 
`r pfs$basic_counts$n_cities_analyzed` municipal police departments.

>>>>

We have collected and released a dataset of 
`r pfs$basic_counts$collected$n_stops` traffic stops carried out by 
`r pfs$basic_counts$collected$n_states` state patrol agencies and 
`r pfs$basic_counts$collectec$n_cities` municipal police departments.

We analyzed a unique dataset detailing 
`r pfs$basic_counts$analyzed$n_stops` traffic stops carried out by 
`r pfs$basic_counts$analyzed$n_states` state patrol agencies and 
`r pfs$basic_counts$analyzed$n_cities` municipal police departments.
